### 2023-05-15 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
\begin{figure}[H]
    \centering
    \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
    \caption{\label{fig:schematic}\small A single multicomponent vesicle with boundary $\gamma$ suspended in a domain $\Omega$ with boundary $\Gamma$. The dark red regions are the ``stiff" regions corresponding to the maximum bending stiffness $b_{\max}=1$. The dark blue regions are the ``floppy" regions corresponding to the minimum bending stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a combination of phase, bending, and tension energies, and an imposed flow on $\Gamma$. }
\end{figure}
The fluid is assumed to have zero Reynolds number and is therefore governed by the incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \llbracket \TT\nn \rrbracket = \ff, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$.

We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale
is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is
$b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2
= 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a dimensionless maximum imposed
velocity, $\chi$, which sets a capillary number, and $W$ is the
dimensionless width of the channel at the inlet and outlet. From this
point onwards, all equations are dimenisionless.

On the multicomponet vesicle $\gamma$ the velocity satisfies the no-slip boundary condition
$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.

@@

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass. To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
\begin{align}
    b(u) = (1-u) + \beta u.
    \label{eqn:linearBending}
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta$ is small and the vesicle is confined to a narrow region.
Therefore, in this work we parameterize the bending modulus as
\begin{align}
    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
           \frac{\beta + 1}{2}.
    \label{eqn:tanhBending}
\end{align}
This maps the local minimums of the
double-well potential close to $\beta$ and $1$, but more
importantly, b(u) remains bounded in $(\beta,1)$ even when $u
\notin [0,1]$ (Figure~\ref{fig:concModels}(a)). To demonstrate the
necessity of this new bending model, we consider a multicomponent
vesicle in strong confinement with both bending
models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
maximum value of $u \approx 1.002$ which results in a  minimum bending
stiffness of $b(u) \approx \beta$. However, if we use the linear bending
model~\eqref{eqn:linearBending}, the lipid concentration achieves a
maximum value of $u \approx 1.52$ which results in an unphysical
negative bending stiffness of $b(u) \approx -0.5$. The corresponding
vesicle shape is in Figure~\ref{fig:concModels}(b), and the instability
caused by the negative bending stiffness is near the region with
negative curvature.
%\begin{figure}[htp]
%  \centering
%%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
%  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
%%    \end{tabular}
%\caption{\label{fig:bendingModels} \small A multicomponent vesicle
%  entering a closely-fitting channel using (a) the new bending
%  model~\eqref{eqn:tanhBending}; (b) the linear
%  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
%  bending modulus becomes negative, and this introduces an instability
%  that first appears near the point with the largest negative curvature.
%  The two plots are not at the same time step.}
%\end{figure}

@@

%\begin{figure}[h]
\begin{figure*}[b]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through a stenosed
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent.}
%\end{figure}
\end{figure*}

We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
closely-fitting channel, with a dimensionless maximum velocity of $\chi
= 0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a
multicomponent vesicle with an initially random distribution of lipids
(c). In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. The main difference between the two reduced
areas is that the vesicles with smaller reduced area undergo
tank-treading motions. As mentioned earlier, tank treading occurs when
the top and bottom lubrication layers differ in size. The size of the
lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.

%\begin{figure}[h]
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through a stenosed
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent. The multicomponent
  vesicle travels slightly faster, so it leaves the stenosed region
  earlier than the single-component cases (see
  Figure~\ref{fig:vesVelocity}).}
%\end{figure}
\end{figure*}

@@

While the size of the lubrication layers affect the tank-treading behavior and the excess pressure, it has almost no effect on the migration speed of the vesicle. In Figure~\ref{fig:vesVelocity}, we plot the average velocity of the vesicle as it passes through the stenosed region. With the exception of the single-component vesicle with $b=1$ and $\alpha = 0.6$, the average vesicle speed is constant. Obviously, this average velocity would be affected by the maximum imposed velocity, $\chi$.

@@

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension (yellow), and phase (red) energies for a (a/b) single-component vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$, and (e/f) multicomponent vesicle. The reduced areas are $alpha = 0.4$ (a/c/e) and $\alpha = 0.6$ (b/d/f).}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
     \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle with 50\% floppy region passing through a contracting geometry. The vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) the initial lipid-species distribution is fully separated on the right side of the vesicle; (b) the initial lipid-species distribution is randomly distributed (not fully separated) on the vesicle membrane; (d) the initial lipid-species distribution is fully separated on the left side of the vesicle. The vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions. The vesicle either completely or partially reorients itself so that the floppy region is in the back and the stiff region is in the front.}
\end{figure}

@@

In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha = 0.5$ and the dimensionless flow rate is $\chi = 0.25$. We start with a single-component vesicle and then increase the percentage of the vesicle membrane that is floppy. By comparing the vesicle location at the time step just before the vesicle passes through the constriction, we can immediately see that vesicles with membranes that have larger percentage of floppy regions reach and pass through the neck earlier. The dimensionless times that the entire vesicle first passes through the neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
     \caption{\label{fig:RA5} \small A vesicle passing through a contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and the dimensionless maximum velocity is $\chi = 0.25$. The vesicles are: (a) single-component with bending modulus $b=1$; (b) multicomponent with 15\% floppy region; (c) multicomponent with 25\% floppy region; (d) multicomponent with 35\% floppy region; (e) multicomponent with 45\% floppy region. The vesicles with a larger percentage of floppy regions pass through the neck earlier than the vesicles with less percentage of floppy regions.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
\begin{itemize}
  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
  \item Line on vesicle is too thick and change color scheme to same as
    Fig 2
  \item Change to a confined geometry that we use (stenosis)
  \item Show a couple of vesicle shapes and the parabolic profile at
    the inlet, outlet, and in the middle
\end{itemize}

We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
\begin{figure}[H]
  \centering
  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A single multicomponent vesicle
  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
  are the ``floppy'' regions corresponding to the minimum bending
  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
  combination of phase, bending, and tension energies, and an imposed
  flow on $\Gamma$. }
\end{figure}
The fluid is assumed to have zero Reynolds number and is therefore governed by the incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \llbracket \TT\nn \rrbracket = \ff, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$.

We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale
is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is
$b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2
= 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a dimensionless maximum imposed
velocity, $U$, which sets a capillary number, and $W$ is the
dimensionless width of the channel at the inlet and outlet. From this
point onwards, all equations are dimenisionless.

On the multicomponet vesicle $\gamma$ the velocity satisfies the no-slip boundary condition
$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.
\todo[inline]{Need to define capillary number and diffusion time scale.}

@@

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass. To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
\begin{align}
    b(u) = (1-u) + \beta u.
    \label{eqn:linearBending}
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
region.  Therefore, in this work we parameterize the bending modulus as
\begin{align}
    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
           \frac{\beta + 1}{2}.
    \label{eqn:tanhBending}
\end{align}
This maps the local minimums of the
double-well potential close to $\beta$ and $1$, but more
importantly, b(u) remains bounded in $(\beta,1)$ even when $u
\notin [0,1]$ (Figure~\ref{fig:concModels}(a)). To demonstrate the
necessity of this new bending model, we consider a multicomponent
vesicle in strong confinement with both bending
models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
maximum value of $u \approx 1.002$ which results in a  minimum bending
stiffness of $b(u) \approx \beta$. However, if we use the linear bending
model~\eqref{eqn:linearBending}, the lipid concentration achieves a
maximum value of $u \approx 1.52$ which results in an unphysical
negative bending stiffness of $b(u) \approx -0.5$. The corresponding
vesicle shape is in Figure~\ref{fig:concModels}(b), and the instability
caused by the negative bending stiffness is near the region with
negative curvature.
%\begin{figure}[htp]
%  \centering
%%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
%  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
%%    \end{tabular}
%\caption{\label{fig:bendingModels} \small A multicomponent vesicle
%  entering a closely-fitting channel using (a) the new bending
%  model~\eqref{eqn:tanhBending}; (b) the linear
%  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
%  bending modulus becomes negative, and this introduces an instability
%  that first appears near the point with the largest negative curvature.
%  The two plots are not at the same time step.}
%\end{figure}

@@

%\begin{figure}[h]
\begin{figure*}[b]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig5a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig5b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig5c.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through a stenosed
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent.}
%\end{figure}
\end{figure*}

We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
closely-fitting channel, with a dimensionless maximum velocity of $U =
0.25$. Figure~\ref{fig:RA6} shows six time steps of a single-component
vesicle with bending stiffness (a) $b=1$ and (b) $b=0.55$, and a
multicomponent vesicle with an initially random distribution of lipids
(c). In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. The main difference between the two reduced
areas is that the vesicles with smaller reduced area undergo
tank-treading motions. As mentioned earlier, tank treading occurs when
the top and bottom lubrication layers differ in size. The size of the
lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.

%\begin{figure}[h]
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through a stenosed
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  dimensionless maximum velocity is $U = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=1$; (b) single-component with
  bending modulus $b=0.55$; (c) multicomponent. The multicomponent
  vesicle travels slightly faster, so it leaves the stenosed region
  earlier than the single-component cases (see
  Figure~\ref{fig:vesVelocity}).}
%\end{figure}
\end{figure*}

@@

While the size of the lubrication layers affect the tank-treading
behavior and the excess pressure, it has almost no effect on the
migration speed of the vesicle. In Figure~\ref{fig:vesVelocity}, we plot
the average velocity of the vesicle as it passes through the stenosed
region. With the exception of the single-component vesicle with $b=1$
and $\alpha = 0.6$, the average vesicle speed is constant. Obviously,
this average velocity would be affected by the maximum imposed velocity,
$U$.

@@

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension
  (yellow), and phase (red) energies for a (a/b) single-component
  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum
  velocity is $U = 0.25$. The vesicles are: (a) the initial
  lipid-species distribution is fully separated on the right side of the
  vesicle; (b) the initial lipid-species distribution is randomly
  distributed (not fully separated) on the vesicle membrane; (d) the
  initial lipid-species distribution is fully separated on the left side
  of the vesicle. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions. The vesicle either completely or
  partially reorients itself so that the floppy region is in the back
  and the stiff region is in the front.}
\end{figure}

@@

In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
= 0.5$ and the dimensionless flow rate is $U = 0.25$. We start with a
single-component vesicle and then increase the percentage of the vesicle
membrane that is floppy. By comparing the vesicle location at the time
step just before the vesicle passes through the constriction, we can
immediately see that vesicles with membranes that have larger percentage
of floppy regions reach and pass through the neck earlier. The
dimensionless times that the entire vesicle first passes through the
neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the dimensionless maximum velocity is $U = 0.25$. The vesicles are:
  (a) single-component with bending modulus $b=1$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}
